A data-driven study of cystic fibrosis treatment: identifying sub-types of physiotherapy style and physical activity using unsupervised clustering

### 2019-08-16 draft.tex
Adding Fitbit info to appendix

>>>>

\appendix
\section{Appendix : Table of physical activity data features}

\begin{table}[h]
  \caption{Physical activity features}
  \label{fitbit_features}
  \centering
  \begin{tabular}{ |l|l|l| }
    \toprule
    \cmidrule(r){1-2}
    Feature Name & Feature description & Waveform extracted from \\
    \midrule
    userif & 1099 & 0.95 \\
    \bottomrule
    \end{tabular}
\end{table}

\section{Appendix : Cluster metrics for physical activity data}

The tables below show the metrics for the clusters identified for the physical activity data.

\textbf{Steps clusters}

Calinski-harabasz index for the steps clusters is 6021.14 .

\begin{table}[h]
  \caption{Steps clusters Metrics}
  \label{steps_metrics}
  \centering
  \begin{tabular}{ |l|c|c|}
    \toprule
    \cmidrule(r){1-2}
    Cluster name & Cluster Size & Average Silhouette width \\
    \midrule
    XS & 1099 & 0.95 \\
    S & 3942 & 0.34 \\
    M & 2737 & 0.27 \\
    L & 1982 & 0.24 \\
    \bottomrule
    \end{tabular}
\end{table}

\textbf{Heartrate clusters}

Calinski-harabasz index for the heartrate clusters is 5090.37 .

\begin{table}[h]
  \caption{Heartrate clusters Metrics}
  \label{hr_metrics}
  \centering
  \begin{tabular}{ |l|c|c|}
    \toprule
    \cmidrule(r){1-2}
    Cluster name & Cluster Size & Average Silhouette width \\
    \midrule
    S & 1246 & 0.28 \\
    SM & 1640 & 0.2 \\
    M1 & 2308 & 0.21 \\
    M2 & 2584 & 0.26 \\
    L & 1982 & 0.33 \\
    \bottomrule
    \end{tabular}
\end{table}
